---
title: "lesson5exercise"
output: html_notebook
---
# 带有分面和颜色的价格直方图

> Create a histogram of diamond prices.
> Facet the histogram by diamond color
> and use cut to color the histogram bars.

```{r}
library(ggplot2)
data(diamonds)
names(diamonds)

ggplot(aes(x = log(price)), data = diamonds) +
  geom_histogram(aes(color = cut)) +
  scale_fill_brewer(type = "qual") +
  facet_wrap( ~ color)
  
```

```{r}
?scale_fill_brewer

ggplot(aes(x = price), data = diamonds) +
  geom_histogram(aes(color = cut)) +
  scale_fill_brewer(type = "qual",palette = 2) +
  scale_x_log10() +
  facet_wrap( ~ color)
```
---

# 价格与按切工填色的表格 
> Create a scatterplot of diamond price vs.table and color the points by the cut of the diamond.

> In the link, a color palette of type 'qual' was used to color the scatterplot using scale_color_brewer(type = 'qual')

```{r}
ggplot(aes(x=table, y = price), data = diamonds) +
  geom_point(aes(color = cut)) +
  scale_fill_brewer(type = "qual") +
  scale_x_continuous(breaks = seq(50, 80, 2)) +
  xlim(c(48, 82))
```
```{r}
ggplot(aes(x=table, y = price), data = diamonds) +
  geom_point(aes(color = cut)) +
  scale_fill_brewer(type = "qual") +
  scale_x_continuous(breaks = seq(50, 80, 2), limits = c(48, 82))
```

---
# 典型表值

![image](https://s3.cn-north-1.amazonaws.com.cn/u-img/862829572)

大多数完美切工钻石的典型表范围是多少？ 至 大多数优质切工钻石的典型表范围是多少？ 至 使用你在之前练习中创建的图表查看答案。无需进行汇总。

**这道题的本意实际上是通过观察上一节课所绘制的图形来得到答案。**
[53,57]

[58,62]

# 价格与体积和钻石净度

> Create a scatterplot of diamond price vs.volume (x * y * z) and color the points by the clarity of diamonds.
> Use scale on the y-axis to take the log10 of price. You should also omit the top 1% of diamond volumes from the plot.
> Note: Volume is a very rough approximation of a diamond's actual volume.
> Note: In the link, a color palette of type 'div' was used to color the scatterplot using scale_color_brewer(type = 'div')

**去掉（忽略）前1%的值方法**

- 可以再scale_x_continous里使用quantile。


```
scale_x_continuous(limits = c(0, quantile(diamonds$Volume, 0.99)))
```
- 同样可以在图层xlim，ylim中使用quantile()函数

```{r}
diamonds$volume <- with(diamonds, x * y * z)
head(diamonds)

ggplot(aes(x=volume, y=log10(price)), data = diamonds) +
  geom_point(aes(color=clarity)) +
  scale_color_brewer(type = 'div') +
  scale_x_continuous(limits = c(0, quantile(diamonds$volume, 0.99)))


ggplot(aes(x=volume, price), data = diamonds) +
  geom_point(aes(color=clarity)) +
  scale_color_brewer(type = 'div') +
  xlim(c(0, quantile(diamonds$volume, 0.99))) +
  scale_y_log10()

```

# 新建友谊的比例

> Your task is to create a new variable called 'prop_initiated'  in the Pseudo-Facebook data set. The variable should contain the proportion of friendships that the user initiated.

```{r}
pf <- read.delim('pseudo_facebook.tsv')

pf$prop_initiated = with(pf, friendships_initiated / friend_count)

str(pf)
```

# prop_initiated 与使用时长

> Create a line graph of the median proportion of friendships initiated ('prop_initiated') vs. tenure and color the line segment by year_joined.bucket.

> Recall, we created year_joined.bucket in Lesson 5 by first creating year_joined from the variable tenure. Then, we used the cut function on year_joined to create four bins or cohorts of users.

> (2004, 2009]  (2009, 2011]  (2011, 2012]  (2012, 2014]
  
  
```{r}
pf$year_joined <- with(pf, floor(2014 - tenure/365))
head(pf$year_joined, 20)
pf$year_joined.bucket = cut(pf$year_joined, c(2004,2009,2011,2012,2014))

ggplot(aes(x=tenure, y=prop_initiated), data = subset(pf, !is.na(year_joined.bucket)&!is.na(prop_initiated))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
  
```

# 平滑化 prop_initiated 与使用时长

> Smooth the last plot you created of of prop_initiated vs tenure colored by year_joined.bucket. 
> You can bin together ranges of tenure or add a smoother to the plot.

```{r}
ggplot(aes(x=7 * round(tenure/7), y=prop_initiated), data = subset(pf, !is.na(year_joined.bucket)&!is.na(prop_initiated))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)

ggplot(aes(x=30 * round(tenure/30), y=prop_initiated), data = subset(pf, !is.na(year_joined.bucket)&!is.na(prop_initiated))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```
# 最大的 prop_initiated 组

平均来说，哪个组发起的 Facebook 好友请求比例最大？你在上个练习中创建的带平滑器的图可以帮你回答这个问题。 ○ 在 2009 年之前加入的人 ○ 在 2009 年至 2011 年之间加入的人 ○ 在 2011 年至 2012 年之间加入的人 ○ 在 2012 后加入的人

![image](https://s3.cn-north-1.amazonaws.com.cn/u-img/862129720)

[12,~]

# 最大的组均值 prop_initiated

- 对于发起好友请求比例最大的组，这个组的平均（即均值）好友请求比例是多少？
 
- 你认为该组发起的好友请求比例大于其他组的原因是什么？

```{r}
library(dplyr)

pf %>% group_by(year_joined.bucket) %>%
  filter(!is.na(year_joined.bucket)) %>%
  filter(!is.na(prop_initiated)) %>%
  summarise(mean_prop_initiated = mean(prop_initiated))
```


![image](https://s3.cn-north-1.amazonaws.com.cn/u-img/869108880)

0.67

# 经过分组、分面和填色的价格/克拉

> Create a scatter plot of the price/carat ratio of diamonds. The variable x should be assigned to cut. The points should be colored by diamond color, and the plot should be faceted by clarity.

```{r}
names(diamonds)
ggplot(aes(x=cut, y=price/carat), data = diamonds) +
  geom_point(aes(color = color)) +
  facet_wrap( ~ clarity) +
  scale_color_brewer(type = 'div')
```

# Gapminder 多变量分析






